---
title: "Homework 1"
author: Zhongqi Yue
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character and factor.

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

"as.numeric" works for the random sample and logical vector but not character and factor, which explains why I cannot take the mean for them.

```{r try_convert the logical vector and multiply the random sample by the result}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df,samp)
as.factor(pull(prob1_df, samp_gt_0)) 
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df,samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) 
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df,samp)
```

I can multiply the random sample by the result to the logical vector which is converted to numeric but not to factor. But if I convert the logical vector to a factor and then convert the result to numeric, I can multiply the random sample by the result.

## Problem 2
```{r}
data("penguins", package = "palmerpenguins")
```

#### The short description of the data set
```{r dataset_size}
prob2_df = (force(penguins))
levels(pull(prob2_df, species))
as.numeric(pull(prob2_df, species))
levels(pull(prob2_df, island))
as.numeric(pull(prob2_df, island))
levels(pull(prob2_df, sex))
range(pull(prob2_df, bill_length_mm),na.rm = TRUE)
range(pull(prob2_df, bill_depth_mm),na.rm = TRUE)
range(pull(prob2_df, flipper_length_mm),na.rm = TRUE)
range(pull(prob2_df, body_mass_g),na.rm = TRUE)
range(pull(prob2_df, year),na.rm = TRUE)
nrow(prob2_df)
ncol(prob2_df)
mean(pull(prob2_df, flipper_length_mm), na.rm = TRUE)
```


This data set has 344 observations and 8 variables which are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year. There are three species: 152 Adelie, 52 of which are on Torgersen island, 44 of which are on Biscoe island, 56 of which are on Dream island; 124 Gentoo, all of which are on Biscoe island; and 68 Chinstrap, all of which are on Dream island. These three species are also divided by sex as male and female.The value of bill length ranges from 32.1mm to 59.6mm. The value of bill depth ranges from 13.1mm to 21.5mm. The value of flipper length ranges from 172mm to 231mm. The value of body mass ranges from 2700g to 6300g. The investigation are taken between year 2007 and 2009. The data set has 334 rows and 8 columns. Additionally, the mean flipper length is 200.9152 mm.

#### The scatterplot of flipper_length_mm (y) vs bill_length_mm (x)
```{r prob2_plot}
ggplot(prob2_df, aes(y = flipper_length_mm, x = bill_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 4)
```

