---
title: "Homework 1"
author: Zhongqi Yue
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character and factor.

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

"as.numeric" works for the random sample and logical vector but not character and factor, which explains why I cannot take the mean for them.

```{r try_convert the logical vector and multiply the random sample by the result}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df,samp)
as.factor(pull(prob1_df, samp_gt_0)) 
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df,samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) 
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df,samp)
```

I can multiply the random sample by the result to the logical vector which is converted to numeric but not to factor. But if I convert the logical vector to a factor and then convert the result to numeric, I can multiply the random sample by the result.

## Problem 2